Analyzing the impact of social attributes on the success of commit integration

### 2017-02-17 Paper/MSRChallenge2017.tex
some threats to validity and table

\textbf{Related work:}
Similar studies have shown the relationship between different attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al~\cite{tsay14icse} performed a very relevant study where they 
determine that the social connection between the developer who is asking the 
pull request and the integrators is a key factor torwards acceptance of a pull 
request. Unlike this previous study, in our study we look at a broader aspect of 
social aspects and how this attributes towards the success in Travis CI jobs. 
Gousios et al~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer requesting the changes to be pulled 
and the acceptance rate of these changes is highly correlated. Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request. Bettenburgh et 
al~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to the automatic build process. Yu et al~\cite{yu16} 
analyze the impact of CI usage in Github and its correlation with software 
quality. Unlike the before mentioned, our study focuses on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes. %, and not 
interactions between developers, or technical properties of the project.

@@

\section{Evaluation}
To evaluate the predictive power we can gain from analyzing the corpus 
provided~\cite{msr17challenge}, we have created a logistic regression model from 
both the datasets described in Section \ref{approach}. A logistic regression 
model is one where the dependent variable is categorial~\cite{freedman09}. Since 
in this study we are interested only in the cases where the commit was 
successfully integrated against any other possible state (errored, failed, 
canceled, started), we have divided our corpus into only two possible states, 
successful and notSuccessful, as to have a binary dependent variable.

@@

\section{Results}
Results \todo{maybe this section can be merged with the prior one}

@@

@@

\textbf{Internal}

\textbf{External}

\textbf{Structural}

>>>>

\textbf{Related work:}
Similar studies have shown the relationship between different attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al~\cite{tsay14icse} performed a very relevant study where they 
determine that the social connection between the developer who is asking the 
pull request and the integrators is a key factor torwards acceptance of a pull 
request. Unlike this previous study, in our study we look at a broader aspect of 
social aspects and how this attributes towards the success in Travis CI jobs. 
Gousios et al~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer requesting the changes to be pulled 
and the acceptance rate of these changes is highly correlated. Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request. Bettenburgh et 
al~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al~\cite{vasilescu14} explored how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to the automatic build process. Yu et al~\cite{yu16} 
analyze the impact of CI usage in Github and its correlation with software 
quality. Unlike the before mentioned, our study focuses on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.
%, and not 
%interactions between developers, or technical properties of the project.

\todo{Contributions}

@@

\todo{Explain downsampling}

\section{Evaluation}
\todo{I guess we have to remove the logisitic regression section here if we are not going to present those results. Depending on what Bogdan and Claire think.}
To evaluate the predictive power we can gain from analyzing the corpus 
provided~\cite{msr17challenge}, we have created a logistic regression model from 
both the datasets described in Section \ref{approach}. A logistic regression 
model is one where the dependent variable is categorial~\cite{freedman09}. Since 
in this study we are interested only in the cases where the commit was 
successfully integrated against any other possible state (errored, failed, 
canceled, started), we have divided our corpus into only two possible states, 
successful and notSuccessful, as to have a binary dependent variable.

@@

\section{Results}
Results \todo{maybe this section can be merged with the prior one} Table \ref{resultsTable}

\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Original number of instances}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

\textbf{Incorrectly Classified Instances}&  22.99\% & 18.90\% & 35.90\% & 23.91\%\\

\textbf{Kappa statistic}& 0.21 &  0.42 & 0.28  & 0.52 \\

\textbf{Mean absolute error}& 0.34 &  0.28 & 0.43 & 0.32\\

\textbf{Relative absolute error}& 88.64\% & 72.42\%  & 85.35\% & 63.07\%\\
\hline
\textbf{Increase when adding social attributes}& \multicolumn{2}{|c||}{4.09\%}  & \multicolumn{2}{|c}{11.99\%}\\

\hline
\end{tabular}
\\
\center
  \caption{ Second and third columns: Comparison of performance when running 10 fold cross validation of two decision trees. The first column after the first double bar uses only technical attributes to predict the Travis Job status, the second column augments the dataset with social attributes. Fourth and fifth columns: The same intuition as the previous two, with the difference that the dataset was downsampled to provide the same number of successful and unsuccessful instances }
  \label{resultsTable}
\end{table*}

@@

\noindent\textbf{Internal validity:}
The internal validity threats deal with possible errors in our implementation and experiments.
The researchers in this study used the dataset provided by the MSRChallenge~\cite{msr17challenge} to gain useful information regarding the behavior of developers when pushing commits and how well these commits integrate successfully with the project. The authors have used Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for usage of machine learning algorithms to analyze our datasets. We are aware that, as every human written tool, Weka is prone to contain errors and/or bugs; nonetheless, Weka is a broadly used, open source tool that is subject to high quality standards and a vast user and developer base which makes it more likely to be a high quality code and to have less bugs than lesser used tools.

The scripts we have created to adapt and extract the datasets we needed, and the scripts to obtain the developer social data are publicly available to facilitate the transparency and quality of the process.\footnote{https://goo.gl/CqTX44}

\noindent\textbf{External validity:} 
External validity threats deal with the generalizability of our findings. 
To tackle the concern that the results of this study might not generalize to other studies outside of the studied cases, we have used a broad and rich dataset~\cite{msr17challenge} in our analysis.

\noindent\textbf{Construct validity:}
Regarding the suitability of our evaluation metrics,

@@
